Next Trippy Structures\thanks{Supported by organization x.}

### 2019-01-16 paper.tex
Done with NewCTR

@@

Explain variations with less restricted queries.

Theoretically we can answer anything. It's a representation, after all...

 \Fn{\fxy{\la,\lz,\sa,\sz,\ta,\tz,\n}}{
 \KwData{lines \la,\lz, stops \sa,\sz, times \ta,\tz and length of the sequence \n}
 \KwResult{Number of occurences}
 \BlankLine
 \pattern $\leftarrow \{\sz,0,\sa\}$\;
 \left,\right $\leftarrow$ \GetRange{\csa, $0$, \n, \pattern}\;
 \leftzero $\leftarrow$ \GetPsi{\csa, \left}\;
 \rightzero $\leftarrow$ \GetPsi{\csa, \right}\;
 \tcp{\right-\left = \rightzero-\leftzero}
 \a,\z $\leftarrow$ \GetRange{\wml{$0$},\leftzero,\rightzero,\la}\;
 \ja,\jz $\leftarrow$ \GetJCodes{\la,\sa,\ta,\tz}\;
 \a,\z $\leftarrow$ \GetRangeSpecial{\wmj,\a,\z,\ja,\jz}\;
 \ap $\leftarrow$ \TrackUp{\wml{$0$},\a}\;
 \zp $\leftarrow$ \TrackUp{\wml{$0$},\z}\;
 \tcp{\z-\a = \zp-\ap}
 \offset $\leftarrow$ \Select{\csa,\sz}\;
 \a,\z $\leftarrow$ \GetRange{\wml{\sz},\left-\offset~$+$~\ap-\leftzero,
 \left-\offset~$+$~\ap-\leftzero,\lz}\;
 \ja,\jz $\leftarrow$ \GetJCodes{\lz,\sz,\ta,\tz}\;
 \Return{\GetCount{\wmj,\offset~+~\a,\offset~+~\z,\ja,\jz}}\;
 }

\section{Experiments}
For space, I propose to compare with our previous structures and with a plain representation using bits per symbol (bps). Otherwise, the baseline we select for our $\%$ can be misleading.

>>>>

 \Fn{\fxy{\la,\lz,\sa,\sz,\ta,\tz,\n}}{
 \KwData{lines \la,\lz, stops \sa,\sz, times \ta,\tz and length of the sequence \n}
 \KwResult{Number of occurences}
 \BlankLine
 \pattern $\leftarrow \{\sz,0,\sa\}$\;
 \left,\right $\leftarrow$ \GetRange{\csa, $0$, \n, \pattern}\;
 \leftzero $\leftarrow$ \GetPsi{\csa, \left}\;
 \rightzero $\leftarrow$ \GetPsi{\csa, \right}\;
 \tcp{\right-\left = \rightzero-\leftzero}
 \a,\z $\leftarrow$ \GetRange{\wml{$0$},\leftzero,\rightzero,\la}\;
 \ja,\jz $\leftarrow$ \GetJCodes{\la,\sa,\ta,\tz}\;
 \a,\z $\leftarrow$ \GetRangeSpecial{\wmj,\a,\z,\ja,\jz}\;
 \ap $\leftarrow$ \TrackUp{\wml{$0$},\a}\;
 \zp $\leftarrow$ \TrackUp{\wml{$0$},\z}\;
 \tcp{\z-\a = \zp-\ap}
 \offset $\leftarrow$ \Select{\csa,\sz}\;
 \a,\z $\leftarrow$ \GetRange{\wml{\sz},\left-\offset~$+$~\ap-\leftzero,
 \left-\offset~$+$~\zp-\leftzero,\lz}\;
 \ja,\jz $\leftarrow$ \GetJCodes{\lz,\sz,\ta,\tz}\;
 \Return{\GetCount{\wmj,\offset~+~\a,\offset~+~\z,\ja,\jz}}\;
 }

@@

It is trivial to reuse the Algorithm~\ref{alg:xy} to answer queries with less constrains. For example, if we were only interested in restricting the starting line, we could return \DataSty{z}-\DataSty{a} after line 7. Or if we only wanted to restrict the ending line and time, we can do it by skipping the lines 4-12, and using directly \FuncSty{GetRange}{(\FuncSty{WML}{(s$_z$)},left-offset,right-offset,l$_z$)} in line 14. The complexity would increase if we restricted by a time window but not by lines, as would need to iterate through all possible lines for \DataSty{s$_a$} and \DataSty{s$_z$} to obtain the jcodes for each line and perform these operations on (ii) and (iii). Fortunately, the number of lines that a single stop can belong to tends to be rather small in practice, thus with a careful implementation that avoids repeating computation the performance of such query can remain competitive, as will be shown later in Section~\ref{sec:exp}. Finally, to obtain only the trips that started on a given stop we would simply need to set \DataSty{pattern} to $\{0,s_a\}$ in line 2, or alternatively to $\{s_z,0\}$ for the final stop, and skipping the operations on the sections of \DataSty{s$_z$} or $\$$, respectively.

Of course, \ctr can also be used to efficiently obtain other interesting information about trips, such as the top k most boarded stops, as shown in \cite{brisaboa2018compact}, with the additional possibility of differentiating stops that are only used to switch lines in \ctr. However, there is no known way of using this structure to obtain other kinds of information efficiently (e.g. the number of passengers in a journey between two stops).

\section{Experiments}
\label{sec:exp}
For space, I propose to compare with our previous structures and with a plain representation using bits per symbol (bps). Otherwise, the baseline we select for our $\%$ can be misleading.
